### 2019-12-06 Source/Paper 3 - Delphi Review/DelphiEmail.tex
updated final Delphi Email

\documentclass{article}

@@

The following survey is stage 1 of a Delphi questionnaire. This is designed to obtain your personal opinions relating to the problem described above. The Delphi process involves obtaining responses from you on three separate occasions and the we estimate that it should take no more than 30 minutes to respond:

@@

Round 2: Your answers (and those from the other panellists) from round 1 will be summarised and formulated into a series of more specific questions that you will be asked to respond to.

Round 3: Round 2’s questions will be submitted to you again but this time you will also be able to see the average reply of the other panellists and you will then be asked if you would like to adjust your answer from the second round or not. The identity of all panelists will remain confidential at all times.

@@

1) It is estimated that between five and ten minutes of spontaneous speech would be an ideal balance between data quality and ease of providing a sample. 
	a) Do you agree with this? if not, please state why?
	b) What task(s) do you think would be useful for eliciting an appropriate amount of speech?
	c) How often should data be collected that will provide a balance between accurate tracking of language use over time whilst reducing intrusiveness?

2) The aim of the end application is to provide a way for users to provide multiple samples over a period of time, however as with all longitudinal data collection methods will be subject to participant attrition.
	a) In your opinion, how might this application encourage continued submissions of language samples?

3) The aim of creating this mobile application is to facilitate the ease in which a large number of samples can be collected? 
	a) In your opinion, what problems do you foresee happening with this collection method? 
	b) Are there any potential solutions to these problems that spring to mind?

Thanks in advance for your time,

Jomar Alcantara
Aston University
\end{document}

>>>>

\documentclass{letter}
\usepackage{enumerate}

@@

The following survey is stage one of a Delphi questionnaire. This is designed to obtain your personal opinions relating to the problem described above. The Delphi process involves obtaining responses from you on three separate occasions and we estimate that it should take no more than 30 minutes to respond at each stage:

@@

Round Two: Your answers (and those from the other panellists) from round 1 will be summarised and formulated into a series of more specific questions that you will be asked to respond to.

Round Three: Round Two’s questions will be submitted to you again but this time you will also be able to see the average reply of the other panellists and you will then be asked if you would like to adjust your answer from the second round or not. The identity of all panellists will remain confidential at all times.

@@

1) Literature suggests that between five and ten minutes of spontaneous speech would be an ideal balance between data quality and ease of providing a sample. 
\begin{enumerate}[(a)]
	\item Do you agree with this? if not, please state why.
	\item What task(s) do you think would be useful for eliciting an appropriate amount of speech? For example. Picture Description task
	\item How often should data be collected that will provide a balance between accurate tracking of language use over time whilst reducing intrusiveness?
\end{enumerate}

2) The aim of the end application is to provide a way for users to provide multiple samples over a period of time, however as with all longitudinal data collection methods it will be subject to participant attrition.
\begin{enumerate}[(a)]
	\item In your opinion, how might we encourage continued submissions of language samples?
\end{enumerate}

3) The aim of creating this mobile application is to facilitate the ease with which a large number of samples can be collected? 
\begin{enumerate}[(a)]
	\item In your opinion, what problems do you foresee happening with this collection method? 
	\item Are there any potential solutions to these problems that spring to mind?
\end{enumerate}
Thanks in advance for your time,

Jomar Alcantara

Aston University
\end{document}
